Background
```{r}
library(tidyverse)
source("R/moving-average.R")
```
git co

Data

Raw data from Schaefer et al. downloaded from the EDI data portal
```{r}
BQ1 <- read_csv("data/QuebradaCuenca1-Bisley.csv")
BQ2 <- read_csv("data/QuebradaCuenca2-Bisley.csv")
BQ3 <- read_csv("data/QuebradaCuenca3-Bisley.csv")
RMP <- read_csv("data/RioMameyesPuenteRoto.csv")
```

Binding the four raw data frames
```{r}
BPR <- bind_rows(BQ1, BQ2, BQ3, RMP)
```


Methods

Filtering for sample date and 5 ions: Pottassium, Nitrate, Calcium, Magenesium, and Ammonium.

```{r}
bpr_ions <- BPR |>
  filter(Sample_Date >= "1986-05-16" & Sample_Date < "1995-01-03") |>
  select(Sample_Date, K, `NO3-N`, Mg, Ca, `NH4-N`)
```

Function was created to run the code that assigns 9 week windows and calculates the mean concentration for each ion.
```{r}
result<- function(bpr_ions)
```


The output of this code returns a wide tibble. This code converts the table to long tidy form.

```{r}
result_long <- result |>
  pivot_longer(
    cols = c(K, `NO3-N`, Mg, Ca, `NH4-N`),
    names_to = "Ion",
    values_to = "Concentration (mg/L)"
  )
```



Results

This code creates a plot figure containing 5 graphs. Each graph shows the results of the 9 week moving average analysis of ions sampled at four sites before and after Hurricane Hugo

```{r}
result_long |>
  ggplot(
    mapping = aes(
      x = window_start,
      y = `Concentration (mg/L)`,
      color = Ion
    )
  ) +
  geom_point() +
  geom_line() +
  labs(
    title = "Ion Concentration",
    x = "Year",
    y = "Concentration"
  ) +
  facet_wrap(~Ion, scales = "free", ncol = 1) +
  theme(
    plot.title = element_text(hjust = 0.5)
  )
```
